\documentclass[10pt,conference]{IEEEtran}
\usepackage{adjustbox}
\usepackage{booktabs}

\usepackage{listings}
\usepackage{epsfig}
\usepackage{url}
\usepackage{cite}
\usepackage{fancybox}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{balance}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage{subfig}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage[ruled,linesnumbered]{algorithm2e}
\usepackage[para,online,flushleft]{threeparttable}
\usepackage{xspace}
\usepackage[scaled]{beramono}
\usepackage[T1]{fontenc}



\usepackage[english]{babel} % handle hyphenation

\usepackage{amssymb}
\usepackage{ulem}
\normalem


\newcommand{\cready}[2]{{\color{red}{\ifx&#1&\else- #1\fi}} {\color{green}{\ifx&#2&\else+ #2\fi}}}%
\renewcommand{\cready}[2]{#2}%


\let\oldemptyset\emptyset
\let\emptyset\varnothing

\lstset{
numbers=left,
frame=single,
language=C,
basicstyle=\fontfamily{fvm}\scriptsize,
showlines=true
%xleftmargin=.2\textwidth, xrightmargin=.2\textwidth,
}

\newcommand{\highlight}[1]{\colorbox{yellow}{\textbf{#1}}}
\newcommand{\fixme}[1]{\highlight{FIXME:} \emph{#1}}
\newcommand{\todo}[1]{\highlight{TODO:} \emph{#1}}
\newcommand{\Qinkun}[1]{\highlight{Qinkun's Response:} \emph{#1}}
\newcommand{\jl}[1]{\highlight{JL}{\textbf{#1}}}
\renewcommand{\jl}[1]{}

\newcommand{\cut}[1]{}
\newcommand{\replace}[2]{#2}

\newcommand{\tool}{TANA}
\renewcommand{\tool}{CleverHans}
\renewcommand{\tool}{Cygne}
\renewcommand{\tool}{Do-Re-Mi}
\renewcommand{\tool}{Ta-fa Te-fe}
\renewcommand{\tool}{Ti-ri-ti-ri}
\renewcommand{\tool}{Du-Ta-De-Ta}
\renewcommand{\tool}{\textsf{Abacus}}
\newcommand{\tana}{\tool}

\newtheorem{mydef}{Definition}
\newtheorem{theorem}{Theorem}
%\renewcommand{\baselinestretch}{0.98}\selectfont


% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )


% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}


\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
%\title{\tool{}: Precise, Scalable, and Fine-grained Side-channel Information Leakage Quantification for Production Software}
%\title{\tool{}: Precise and Scalable Fine-grained Side-channel Information Leakage Quantification for Production Software Using Program Analysis and Monte Carlo Sampling}
\title{\tool{}: Precise Side-Channel Analysis}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Qinkun Bao\IEEEauthorrefmark{1},
Zihao Wang\IEEEauthorrefmark{1},
Xiaoting Li\IEEEauthorrefmark{1}, 
James R. Larus\IEEEauthorrefmark{2}, and
Dinghao Wu\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}
The Pennsylvania State University}
\IEEEauthorblockA{\IEEEauthorrefmark{2}EPFL}
}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass




% make the title area
\maketitle



\begin{abstract}

Side-channel attacks allow adversaries to infer sensitive information from non-functional characteristics. Prior side-channel
detection work is able to identify numerous potential vulnerabilities. 
However, in practice, many such vulnerabilities leak a negligible amount of
sensitive information, and thus developers are often reluctant to address
them. Existing tools do not provide information to evaluate a leak's severity, such as the number of
leaked bits.
  
To address this issue, we propose a new program analysis method to precisely quantify the 
leaked information in a single-trace attack through side-channels.
It can identify covert information flows in programs that expose 
confidential information and can reason about security flaws 
that would otherwise be difficult, if not impossible, for a developer to find.
We model an attacker's observation of each leakage site as a constraint.  
We use symbolic execution to generate these
constraints and then run Monte Carlo sampling to estimate the number of leaked
bits for each leakage site. By applying the Central Limit Theorem, 
we provide an error bound for these estimations.
  
We have implemented the technique in a tool called \tool{}, which
not only finds very fine-grained side-channel vulnerabilities but also estimates how many
bits are leaked. \tool{} outperforms existing dynamic side-channel
detection tools in performance and accuracy. 
We evaluate \tool{} on OpenSSL, mbedTLS, Libgcrypt, and Monocypher\@.  
Our results demonstrate that most reported vulnerabilities are difficult to
exploit in practice and should be de-prioritized by developers.
We also find several sensitive vulnerabilities that
are missed by the existing tools. We confirm those vulnerabilities with
manual checks and by contacting the developers.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

% no keywords
\IEEEpeerreviewmaketitle
\pagenumbering{arabic}
\pagestyle{plain}
\input{sections/introduction}
\input{sections/background}
\input{sections/trace_qif}
\input{sections/scalability}
\input{sections/design}
\input{sections/implementation}
\input{sections/evaluation}
\input{sections/discussion}
\input{sections/related_work}
\input{sections/conclusion}

\section{Data Availability}
\cready{}{\tool{} is publicly available at \url{https://github.com/s3team/Abacus}. The repository also contains benchmarks, metadata, and raw results of our experiments.}

\section{Acknowledgement}
We thank Ziqi Wang, Pei Wang, Zhaofeng Chen, and the anonymous reviewers for their valuable feedback. The work was supported in part by the National Science Foundation (NSF) under grant CNS-1652790, and the Office of Naval Research (ONR) under grants N00014-16-1-2912, N00014-16-1-2265, and N00014-17-1-2894. 

%Any opinions, conclusions in the paper do not reflect the views of funding agencies.

\bibliographystyle{IEEEtran}
\bibliography{refs}

%\newpage
%\clearpage
%\appendices
%\setcounter{section}{0}
%\section*{Supplementary Materials to Submission \#63}
%\setcounter{section}{1}
%\setcounter{page}{1}
%\input{sections/appendix}

\end{document}


