\documentclass[conference]{IEEEtran}

\usepackage{listings}
\usepackage{epsfig}
\usepackage{url}
\usepackage{cite}
\usepackage{fancybox}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{balance}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage{subfig}
\usepackage[ruled,linesnumbered]{algorithm2e}

\usepackage[scaled]{beramono}
\usepackage[T1]{fontenc}

\usepackage[english]{babel} % handle hyphenation

\usepackage{amssymb}

\let\oldemptyset\emptyset
\let\emptyset\varnothing

\lstset{
numbers=left,
frame=single,
language=C,
basicstyle=\fontfamily{fvm}\scriptsize,
showlines=true
%xleftmargin=.2\textwidth, xrightmargin=.2\textwidth,
}

\newcommand{\highlight}[1]{\colorbox{yellow}{\textbf{#1}}}
\newcommand{\fixme}[1]{\highlight{FIXME:} \emph{#1}}
\newcommand{\todo}[1]{\highlight{TODO:} \emph{#1}}
\newcommand{\Qinkun}[1]{\highlight{Qinkun's Response:} \emph{#1}}

\newcommand{\tool}{TANA}
\renewcommand{\tool}{CleverHans}
\renewcommand{\tool}{Cygne}
\renewcommand{\tool}{Do-Re-Mi}
\renewcommand{\tool}{Ta-fa Te-fe}
\renewcommand{\tool}{Ti-ri-ti-ri}
\renewcommand{\tool}{Du-Ta-De-Ta}
\renewcommand{\tool}{\textsf{Abacus}}
\newcommand{\tana}{\tool}

\newtheorem{mydef}{Definition}
\newtheorem{theorem}{Theorem}

\renewcommand{\baselinestretch}{0.97}

\begin{document}

%\title{\tool{}: Precise Fine-grained Side-channel Information Leakage Quantification in Binaries}
\title{\tool{}: Precise, Scalable, and Fine-grained Side-channel Information Leakage Quantification for Production Software}
\author{Anonymous}

\maketitle

\begin{abstract}
    Side-channel attacks allow adversaries to infer sensitive information based
    on non-functional characteristics. Existing work on software side-channel
    detections can identify numerous potential vulnerabilities.
    %side-channel leakage sites.
    However, in practice, many such vulnerabilities leak a negligible amount of
    sensitive information, and thus developers are often reluctant to address
    them.
    %Those leakage sites can leak one bit, two bits, or many bits.
    On the other hand, no existing tools can precisely report the number of
    leaked bits for each leakage site for production systems.

    To overcome this limitation, we propose a novel method to precisely quantify
    the leaked information from side-channel vulnerabilities. Our quantification
    method is dramatically different from previous methods, and the results are
    confirmed to be much more precise and usable in practice. We model each
    leakage as a constraint.
    %  and use these constraints to divide the input space into subsets such
    %  that  %.  Among those subsets, only one subset satisfies every
    %  constraint.  %As we discuss later, The cardinality of the subset
    %  corresponds to the amount of leaked information from those leakages. 
    We scale  symbolic execution to production software to generate the
    constraints
    % It is widely believed that symbolic execution is expensive in terms of
    % performance. We systematically analyze the bottlenecks of the current
    % dynamic symbolic execution approach and make it scalable to real-world
    % crypto systems.
    and then run Monte Carlo sampling to estimate the number of leaked
    information.
    % for each detected vulnerability.
    By using
    %With the help of
    the Central Limit Theorem, we can also give the error bound for estimation.

    We have implemented the above technique in a tool called \tool{}, which can
    not only find the side-channel vulnerabilities but also estimate how many
    bits are leaked.  \tool{} outperforms existing dynamic side-channel
    detection tools in terms of performance and accuracy. Also, \tool{} can
    report a very fined-grained vulnerability leakage information.
    % Compared to existing abstract interpretation approaches that can only give
    % upper leakage bounds, the information reported by our tool is more useful
    % for developers to identify the severity level of each side-channel
    % vulnerability.
    We evaluated \tool{} on OpenSSL and Mbed TLS\@.
    %, and found several severe side-channel vulnerabilities. Compared with
    %previous research, the results are surprisingly different.
    Our results show that most of the reported vulnerabilities are hard to
    exploit in practice.  We also find several sensitive vulnerabilities that
    are missed by the existing tools. We confirmed those vulnerabilities with
    manual checks and by the developers.
    %% which are confirmed with manual checks and software developers. 

\end{abstract}


\IEEEpeerreviewmaketitle
\pagenumbering{arabic}
\pagestyle{plain}

\input{sections/introduction}
\input{sections/background}
\input{sections/trace_qif}
\input{sections/scalability}
\input{sections/design}
\input{sections/implementation}
\input{sections/evaluation}
\input{sections/discussion}
\input{sections/related_work}
\input{sections/conclusion}

\clearpage
\bibliographystyle{IEEEtran}
\bibliography{refs}

\newpage
\appendices
\input{sections/appendix}

\end{document}


